---
title: "Diamonds Exploration"
author: "Haley Mincin"
date: "September 28, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Reading Data
```{r}
mydiamonds=read.csv("diamonds.csv")


```

#Dimensions and names of variables
```{r}
dim(mydiamonds)
nrow(mydiamonds)
ncol(mydiamonds)
```
There are 'r nrow(mydiamonds)' rows in our dataset.

```{r}
colnames(mydiamonds)
mydiamonds=mydiamonds[ ,2:11]
```

After knocking off the first collumn I am now let with 'r ncol(mydiamonds)' columns

#Saving my truncated file
Save(mydiamonds,file="mydiamonds.rda"")

#data structure
```{r}
str(mydiamonds)
```
#Summary
```{r}
summary(mydiamonds)
```

#Number of levels of a factor variable
```{r}

levels(mydiamondsclarity)

```

#Subset
```{r}
fairdiamonds=mydiamonds[mydiamonds$cut=="fair",]

```

#example of a poor example
```{r}
levels(fairdiamondscut)
summary(fairdiamondscut)
```

#refactoring after a suset using a factor varibale 
```{r}
fairdiamonds$cut=factor(fairdiamonds$cut)
summary(fairdiamonds$cut)
```

